\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories

### 2020-09-04 paper/supporting_information.tex
tightened fig s6 width

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/k_optimization}
\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix, using the formula described in \textit{Methods}. This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
\label{fig:k_optimization}
\end{figure}

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=.92\textwidth]{figs/k_optimization}
\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}. This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
\label{fig:k_optimization}
\end{figure}
